---
title: "04262018_SH1_full"
output: html_document
---

# Start up functions
```{r "cleanup", echo = FALSE, eval=FALSE}
# not run in knitted doc
rm(list = ls())
.rs.restartR()
```

```{r "load libraries", echo = FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(plotly)
library(stringr)
library(knitr)
library(readxl)
library(tidyr)
library(purrr)
library(xlsx)
opts_chunk$set(dev=c("png", "pdf"), dev.args=list(pdf = list(encoding="WinAnsi", useDingbats=FALSE)),
  fig.keep="all", fig.path = file.path("plots", "smoky_hollows_SRM")) ### CHANGE PLOT SUFFIX ###
```

# Read and organize data
```{r}
read_srm_export <- function(filename, columns = c("peak_name", "RT.min", "basepeak", "area.cpm", "height.cts", "quantitation")) {
  filename %>% 
    # read excel files
    read_excel(sheet = "Integration", skip = 42, 
               col_names = columns, col_types = rep("text", length(columns))) %>% 
    as_data_frame() %>%
    # remove empty rows
    filter(!is.na(peak_name), peak_name != "n.a.") %>% 
    # convert the relevant numeric columns into numbers
    mutate_at(vars(RT.min, area.cpm, height.cts), as.numeric) %>% 
    # remove useless columns
    select(-basepeak, -quantitation) %>% 
    # add filename info
    mutate(file_id = gsub("\\.xls", "", basename(filename))) %>% 
    select(file_id, everything())
}

# get data
all_data <- 
  # find all excel files ##change name and use new folder for new project
  list.files("data_SH1", recursive = TRUE, full.names = TRUE, pattern = "\\.xls$") %>% 
  # send them to the read method
  lapply(read_srm_export) %>% 
  # combine the data set
  bind_rows() %>% 
  # pull out sample information
  #mutate(sample_id = str_match(all_data$file_id, "TSQ\\d+_GB_(.*)$") %>% { .[,2] }) %>% 
  # get n replicates
  group_by(file_id)
  #mutate(n_replicates = length(unique(file_id)))

```

```{r, echo=FALSE, eval=FALSE}
# file names
all_data$file_id %>% unique() %>%  paste(collapse = "\n") %>% message()
```

# Calculation peak amounts and rock concentrations, ID standards
```{r}
depth_and_rock_info <- read_excel(file.path("metadata", "aliphaticSRM_SH1.xlsx")) %>% 
  rename(tle = `TLE.mg`, maltene = `maltenes.mg`, ref_amount_added.ug = `D4.ug` )%>% 
  filter(!is.na(file_id)) %>%
  filter (process == "yes")
depth_and_rock_info
```

```{r}
data_by_depth <- 
  all_data %>%
  left_join(depth_and_rock_info, by = "file_id") %>% 
  group_by(file_id) %>% 
  mutate(
    n_peaks = n(),
    n_standards = sum(peak_name == "D4 C29 ISTD"),
    ref_area.cpm = area.cpm[peak_name == "D4 C29 ISTD"],
    amount.ug = area.cpm/ref_area.cpm * ref_amount_added.ug,
   
    #Normalize by what you want
    conc_rock.ug_g = amount.ug / rock.g, 
    conc_tle.ug.g = amount.ug / tle,  
    conc_maltene.ug.g = amount.ug / maltene
    
  )%>% ungroup() %>% 
  arrange(file_id, peak_name) 

data_by_depth
```

# Calculate Recovery

## Linear regressions of the calibration curves
```{r}
standard <- read_excel(file.path("metadata", "D4_calibration.xlsx"))   ###read excel

###calibration curve
standard %>% 
  ggplot() +
  aes(x = Known.ng, y = Measured_area.counts, color = calibration) + 
  geom_smooth(method = "lm", alpha = 0.5) +
  geom_point() +
  theme_bw() +
  theme(legend.position = "none") 
 
calibrations <- 
  standard %>% 
  filter(!is.na(calibration)) %>% 
  nest(-calibration) %>% 
  mutate(
    fit = map(data, ~summary(lm(`Measured_area.counts`~ `Known.ng`, data = .x))),
    coefficients = map(fit, "coefficients"),
    intercept = map_dbl(coefficients, `[`, 1, 1),
    intercept_se = map_dbl(coefficients, `[`, 1, 2),
    slope = map_dbl(coefficients, `[`, 2, 1),
    slope_se = map_dbl(coefficients, `[`, 2, 2),
    r2 = map_dbl(fit, "r.squared")
  )

calibrations %>% select(-data, -fit, -coefficients) %>% knitr::kable(d = 3)
```

## Determine yield

These numbers are not useful for anything else.
```{r}
calib_data <-
  data_by_depth %>% 
  # temp
  mutate(calibration = "jan2018") %>% 
  left_join(calibrations, by = "calibration") %>% 
  mutate(
    total_volume.uL = 100,
    total_inject.uL = 1.5,
    ref_amount_inject_expected.ng = (ref_amount_added.ug * 1000)/total_volume.uL * total_inject.uL ,
    ref_amount_inject_measured.ng = (ref_area.cpm - intercept)/slope,
    ref_amount_measured.ug = ((total_volume.uL* ref_amount_inject_measured.ng)/total_inject.uL) * 1/1000,
    yield = (ref_amount_inject_measured.ng/ref_amount_inject_expected.ng) * 100
  )
  
calib_data
```



# Ratios
## Functions for ratios and sums
```{r}
sum_peaks <- function(df, filter_condition, new_peak_name) {
  filter_condition <- sprintf("(%s)", str_c(filter_condition, collapse = "|"))
  filter(df, str_detect(peak_name, filter_condition)) %>% 
    summarize(
      file_id = file_id[1],
      depth = depth[1],
      conc_rock.ug_g = sum(conc_rock.ug_g)
    ) %>% 
    mutate(peak_name = new_peak_name)
}

ratio_peaks <- function(df, filter_top, filter_bottom, new_peak_name) {
  filter_top <- sprintf("(%s)", str_c(filter_top, collapse = "|"))
  filter_bottom <- sprintf("(%s)", str_c(filter_bottom, collapse = "|"))
  filter(df, str_detect(peak_name, filter_top) | str_detect(peak_name, filter_bottom)) %>% 
    summarize(
      file_id = file_id[1],
      depth = depth[1],
      ratio = sum(conc_rock.ug_g[str_detect(peak_name, filter_top)]) / sum(conc_rock.ug_g[str_detect(peak_name, filter_bottom)])
    ) %>% 
    mutate(peak_name = new_peak_name)
}
```

## Combine compounds, calculate ratios 
```{r}
#set values to use for later calculations
final_data1 <- calib_data %>% 
    group_by(file_id) %>% 
        do({
          bind_rows(., 
              #C27_Dia/Reg
                sum_peaks(.,  c("C27 aB 20R ST", "C27 aB 20S ST"), "C27Dia"),      
                sum_peaks(., c("C27 aaa 20R ST", "C27 aaa 20S ST", "C27 aBB 20R ST", "C27 aBB 20S ST", "C27 Ba 20R ST", "C27 Ba 20S ST"), "C27Reg"),
            
              #Total Tricyclics
                sum_peaks(., c("C19 Tri HO", "C20 Tri HO", "C21 Tri HO", "C22 Tri HO", "C23 Tri HO", "C24 Tet HO", "C24 Tri HO", "C25 Tri R+S HO", "C26 Tri R HO", "C26 Tri S HO"), "all_tricyclics"),
            
              #4Me_TriMe
                sum_peaks(., c("4B Me 5a cholestane", "4B Me 24 ethyl 5a cholestane", "4B,23S,24S trimethyl 5a cholestane", "4B,23S,24R trimethyl 5a cholestane", "4B,23R,24S trimethyl 5a cholestane", "4B,23R,24R trimethyl 5a cholestane", "4a Me 5a cholestane", "4a Me 24 ethyl 5a cholestane", "4a,23S,24S trimethyl 5a cholestane", "4a,23S,24R trimethyl 5a cholestane", "4a,23R,24S trimethyl 5a cholestane", "4a,23R,24R trimethyl 5a cholestane"), "4Me_TriMe"),
            
              #allRegSt
                sum_peaks(., c("C26 aBB 20S ST", "C26 aBB 20R ST", "C26 aaa 20S ST", "C26 aaa 20R ST","C27 aBB 20S ST", "C27 aBB 20R ST", "C27 aaa 20S ST", "C27 aaa 20R ST", "C28 aBB 20S ST", "C28 aBB 20R ST", "C28 aaa 20S ST", "C28 aaa 20R ST","C29 aBB 20S ST", "C29 aBB 20R ST", "C29 aaa 20S ST", "C29 aaa 20R ST", "C30 aBB 20 R+S ST", "C30 aaa 20S ST", "C30 aaa 20R ST"), "allRegst"),
            
              #allRegHO
                sum_peaks(., c("Ts C27 HO", "Tm C27 HO", "C27 17B H Ho", "29, 30 C28H bisnor HO", "28, 30 C28 bisnor HO", "C29 Ts HO", "C29 Ba HO", "C29 BB Ho", "C30 aB HO", "C30 BB HO", "C30H Ba HO", "C31 HR Ba HO", "C31 aB HR HO", "C31 aB HS HO", "C31 BB HO", "C32 aB HS HO", "C32 aB HR HO", "C33 aB HS HO", "C33 aB HR HO", "C34 aB HR HO", "C34 aB HS HO", "C35 aB HR HO", "C35 aB HS HO"), "allRegHO") ,
              
              #allDiacholestane
              sum_peaks(., c("20S, 4a Me 13B,17a,H diacholestane", "20R, 4a Me 13B,17a,H diacholestane" , "20R, 4a Me 13a,17B,H diacholestane", "20S, 4a,24 dimethyl 13B,17a,H diacholestane", "20R 4a,24 dimethyl 13B,17a,H diacholestane", "20R, 4a,24 dimethyl 13a,17B,H diacholestane" , "20S, 4a,24 dimethyl 13a,17B,H diacholestane", "4a,24 dimethyl 5a cholestane" , "4B,24 dimethyl 5a cholestane"), "allDiacholestane"), 
              
              #all Steranes
              sum_peaks(., c("C26 Ba 20S ST", "C26 Ba 20R ST", "C26 aBB 20S ST", "C26 aBB 20R ST", "C26 aaa 20S ST", "C26 aaa 20R ST", "C27 aaa 20R ST", "C27 aaa 20S ST", "C27 aBB 20R ST", "C27 aBB 20S ST", "C27 Ba 20R ST", "C27 Ba 20S ST", "C28 Ba 20S ST", "C28 Ba 20R ST", "C28 aBB 20S ST", "C28 aBB 20R ST", "C28 aaa 20S ST", "C28 aaa 20R ST" , "C29 Ba 20S ST", "C29 Ba 20R ST", "C29 aBB 20S ST", "C29 aBB 20R ST", "C29 aaa 20S ST", "C29 aaa 20R ST" , "C30 Ba 20S ST", "C30 Ba 20R ST", "C30 aBB 20(R+S) ST", "C30 aaa 20S ST", "C30 aaa 20R ST", "C30 4a Me 20S ST", "C30 4a Me 20R ST + DINO st", "C30 3B Me BB 20S ST", "C30 3B Me 20S ST + C30 3B Me BB 20R ST" , "C30 3BMe 20R ST", "C30 2aMe 20S ST", "C30 2a Me 20R + 4a Me BB 20S ST" , "4B Me 5a cholestane", "4B Me 24 ethyl 5a cholestane", "4B,23S,24S trimethyl 5a cholestane", "4B,23S,24R trimethyl 5a cholestane", "4B,23R,24S trimethyl 5a cholestane", "4B,23R,24R trimethyl 5a cholestane", "4a Me 5a cholestane", "4a Me 24 ethyl 5a cholestane", "4a,23S,24S trimethyl 5a cholestane", "4a,23S,24R trimethyl 5a cholestane", "4a,23R,24S trimethyl 5a cholestane", "4a,23R,24R trimethyl 5a cholestane", "20S, 4a Me 13B,17a,H diacholestane", "20R, 4a Me 13B,17a,H diacholestane" , "20R, 4a Me 13a,17B,H diacholestane", "20S, 4a,24 dimethyl 13B,17a,H diacholestane", "20R 4a,24 dimethyl 13B,17a,H diacholestane", "20R, 4a,24 dimethyl 13a,17B,H diacholestane" , "20S, 4a,24 dimethyl 13a,17B,H diacholestane", "4a,24 dimethyl 5a cholestane" , "4B,24 dimethyl 5a cholestane"), "allSteranes"),
              
              #everything
              sum_peaks(., c(""), "everything")
            
) }) %>% ungroup()

```

            
```{r}
final_data <- final_data1 %>% 
    group_by(file_id) %>% 
        do({
          bind_rows(., 
           #Source
              #C19/tricyclics
                ratio_peaks(., "C19 Tri HO", "all_tricyclics", "C19/tricyclics"),
              #C20/tricyclics
                ratio_peaks(., "C20 Tri HO", "all_tricyclics", "C20/tricyclics"),
              #C21/tricyclics
                ratio_peaks(., "C21 Tri HO", "all_tricyclics", "C21/tricyclics"),
              #C22/tricyclics
                ratio_peaks(., "C22 Tri HO", "all_tricyclics", "C22/tricyclics"),
              #C23/tricyclics
                ratio_peaks(., "C23 Tri HO", "all_tricyclics", "C23/tricyclics"),
              #C24/tricyclics
                ratio_peaks(., c("C24 Tet HO", "C24 Tri HO"), "all_tricyclics", "C24/tricyclics"),
              #C25/tricyclics
                ratio_peaks(., "C25 Tri R+S HO", "all_tricyclics", "C25/tricyclics"),
              #C26/tricyclics
                ratio_peaks(., c("C26 Tri R HO", "C26 Tri S HO"), "all_tricyclics", "C26/tricyclics"),
              #tricyclics/all
                ratio_peaks(., "all_tricyclics", c(""), "tricyclics/all"),
              #C19/C19+23
                ratio_peaks(., "C19 Tri HO", c("C19 Tri HO", "C23 Tri HO"), "C19/C19+23"),
              #C20/C20+23
                ratio_peaks(., "C20 Tri HO", c("C20 Tri HO", "C23 Tri HO"), "C20/C20+23"),
           
              #Ho/St
                ratio_peaks(., "allRegHO", c("C26 aaa 20S ST", "C26 aaa 20R ST", "C27 aaa 20S ST", "C27 aaa 20R ST", "C28 aaa 20S ST", "C28 aaa 20R ST", "C29 aaa 20S ST", "C29 aaa 20R ST", "C30 aaa 20S ST", "C30 aaa 20R ST"), "Ho/St"),
              #Ho/St%
                ratio_peaks(., "allRegHO", c("C26 aaa 20S ST", "C26 aaa 20R ST", "C27 aaa 20S ST", "C27 aaa 20R ST", "C28 aaa 20S ST", "C28 aaa 20R ST", "C29 aaa 20S ST", "C29 aaa 20R ST", "C30 aaa 20S ST", "C30 aaa 20R ST", "allRegHO" ), "Ho/St%"),
            
              #C31_2MHI
                ratio_peaks(., "C31 2a Me Ho", c("C30 aB HO", "C31 2a Me Ho" ), "C31_2MHI"),
              #C31_35_2MHI
                ratio_peaks(., c("C31 2a Me Ho", "C32 2aMe R HO", "C32 2aMe S HO", "C33 2aMe S HO", "C33 2aMe R HO", "C34 2a Me S HO", "C34 2a Me R HO", "C36 2a Me R HO", "C36 2a Me S HO"), c("C30 aB HO", "C31 2a Me Ho", "C32 2aMe R HO", "C32 2aMe S HO", "C33 2aMe S HO", "C33 2aMe R HO", "C34 2a Me S HO", "C34 2a Me R HO", "C36 2a Me R HO", "C36 2a Me S HO"), "C31_35_2MHI"),
              #C31_2-MHI/C27-C30Steranes
                ratio_peaks(., "C31 2a Me Ho", c("C26 aaa 20S ST", "C26 aaa 20R ST", "C27 aaa 20S ST", "C27 aaa 20R ST" ,"C28 aaa 20S ST", "C28 aaa 20R ST", "C29 aaa 20S ST", "C29 aaa 20R ST", "C30 aaa 20S ST", "C30 aaa 20R ST", "C31 2a Me Ho" ), "C31_2-MHI/C27-C30Steranes"),
              #C31 3-MHI 
                ratio_peaks(., "C31 3B Me HO", c("C31 3B Me HO", "C30 aB HO"), "C31 3-MHI"), 
              #C31_35_3MHI(%)
                 ratio_peaks(., c("C31 3B Me HO", "C32 3B Me S HO", "C32 3B Me R HO", "C32 3B Me Ba 22S+R ST", "C33 3BMe S HO", "C33 3BMe R HO", "C34 3B Me S Ho", "C34 3B Me R HO", "C35 3B Me R HO", "C35 3B Me S HO", "C36 3B Me S HO", "C36 3B Me R HO"), c("C30 aB HO","C31 3B Me HO", "C32 3B Me S HO", "C32 3B Me R HO", "C32 3B Me Ba 22S+R ST", "C33 3BMe S HO", "C33 3BMe R HO", "C34 3B Me S HO", "C34 3B Me R HO", "C35 3B Me R HO", "C35 3B Me S HO", "C36 3B Me S HO", "C36 3B Me R HO" ) ,"C31_35_3MHI(%)"),

              #C29ab/C29ab+C30ab
                 ratio_peaks(., "C29 aB HO", c( "C29 aB HO" , "C30 aB HO"), "C29ab/C29ab+C30ab"), 
              #C29ab/allHoab
                 ratio_peaks(., "C29 aB HO" , c("C35 aB HS HO", "C35 aB HR HO", "C34 aB HS HO", "C34 aB HR HO", "C33 aB HS HO" , "C33 aB HR HO", "C32 aB HR HO", "C32 aB HS HO", "C31 aB HS HO", "C31 aB HR HO", "C30 aB HO", "C29 aB HO"), "C29ab/allHoab"), 
              #C30ab/allHoab 
                 ratio_peaks(., "C30 aB HO" , c("C35 aB HS HO", "C35 aB HR HO", "C34 aB HS HO", "C34 aB HR HO", "C33 aB HS HO" , "C33 aB HR HO", "C32 aB HR HO", "C32 aB HS HO", "C31 aB HS HO", "C31 aB HR HO", "C30 aB HO", "C29 aB HO"), "C30ab/allHoab"), 
              #C31ab/allHoab 
                 ratio_peaks(., c("C31 aB HS HO", "C31 aB HR HO") , c("C35 aB HS HO", "C35 aB HR HO", "C34 aB HS HO", "C34 aB HR HO", "C33 aB HS HO" , "C33 aB HR HO", "C32 aB HR HO", "C32 aB HS HO", "C31 aB HS HO", "C31 aB HR HO", "C30 aB HO", "C29 aB HO"), "C31ab/allHoab"),
              #C32ab/allHoab 
                 ratio_peaks(., c("C32 aB HR HO", "C32 aB HS HO") , c("C35 aB HS HO", "C35 aB HR HO", "C34 aB HS HO", "C34 aB HR HO", "C33 aB HS HO" , "C33 aB HR HO", "C32 aB HR HO", "C32 aB HS HO", "C31 aB HS HO", "C31 aB HR HO", "C30 aB HO", "C29 aB HO"), "C32ab/allHoab"),
              #C33ab/allHoab 
                 ratio_peaks(., c( "C33 aB HS HO" , "C33 aB HR HO") , c("C35 aB HS HO", "C35 aB HR HO", "C34 aB HS HO", "C34 aB HR HO", "C33 aB HS HO" , "C33 aB HR HO", "C32 aB HR HO", "C32 aB HS HO", "C31 aB HS HO", "C31 aB HR HO", "C30 aB HO", "C29 aB HO"), "C33ab/allHoab"),
              #C34ab/allHoab 
                 ratio_peaks(., c( "C34 aB HS HO", "C34 aB HR HO") , c("C35 aB HS HO", "C35 aB HR HO", "C34 aB HS HO", "C34 aB HR HO", "C33 aB HS HO" , "C33 aB HR HO", "C32 aB HR HO", "C32 aB HS HO", "C31 aB HS HO", "C31 aB HR HO", "C30 aB HO", "C29 aB HO"), "C34ab/allHoab"),
              #C35ab/allHoab 
                 ratio_peaks(., c("C35 aB HS HO", "C35 aB HR HO") , c("C35 aB HS HO", "C35 aB HR HO", "C34 aB HS HO", "C34 aB HR HO", "C33 aB HS HO" , "C33 aB HR HO", "C32 aB HR HO", "C32 aB HS HO", "C31 aB HS HO", "C31 aB HR HO", "C30 aB HO", "C29 aB HO"), "C35ab/allHoab"),
              #OleananeIndex
                ratio_peaks(., "Oleanane HO", c("Oleanane HO", "C30 aB HO"), "OleananeIndex"),

              #HHI
                ratio_peaks(., c("C35 aB HS HO", "C35 aB HR HO") , c("C35 aB HS HO", "C35 aB HR HO", "C34 aB HS HO", "C34 aB HR HO", "C33 aB HS HO" , "C33 aB HR HO", "C32 aB HR HO", "C32 aB HS HO", "C31 aB HS HO", "C31 aB HR HO"), "HHI"),
              #C35/C35+C34
                ratio_peaks(., c("C35 aB HS HO", "C35 aB HR HO"), c("C34 aB HS HO", "C34 aB HR HO","C35 aB HS HO", "C35 aB HR HO"), "C35/C35+C34"),
              #GI
                ratio_peaks(., "gamma", c("gamma", "C30 aB HO"), "GI"),
              #28,30BNH/28,30BNH+C30
                ratio_peaks(., "28, 30 C28 bisnor HO", c("28, 30 C28 bisnor HO", "C30 aB HO"), "28,30BNH/28,30BNH+C30") ,
           
           #Source
              #C26St/allSt ##INCLUDES ME's
                ratio_peaks(., c("C26 Ba 20S ST", "C26 Ba 20R ST", "C26 aBB 20S ST", "C26 aBB 20R ST", "C26 aaa 20S ST", "C26 aaa 20R ST"), "allSteranes", "C26St/allSt"), 
              #C27St/allSt
                ratio_peaks(., c("C27 aaa 20R ST", "C27 aaa 20S ST", "C27 aBB 20R ST", "C27 aBB 20S ST", "C27 Ba 20R ST", "C27 Ba 20S ST"), "allSteranes", "C27St/allSt"),
              #C28St/allSt
                ratio_peaks(., c("C28 Ba 20S ST", "C28 Ba 20R ST", "C28 aBB 20S ST", "C28 aBB 20R ST", "C28 aaa 20S ST", "C28 aaa 20R ST"), "allSteranes", "C28St/allSt"),
              #C29St/allSt
                ratio_peaks(., c("C29 Ba 20S ST", "C29 Ba 20R ST", "C29 aBB 20S ST", "C29 aBB 20R ST", "C29 aaa 20S ST", "C29 aaa 20R ST"), "allSteranes", "C29St/allSt"),
              #C30St/allSt (does not include Me's in numerator)
                ratio_peaks(., c("C30 Ba 20S ST", "C30 Ba 20R ST", "C30 aBB 20(R+S) ST", "C30 aaa 20S ST", "C30 aaa 20R ST"), "allSteranes", "C30St/allSt"),
              #C30Me/allSt (C30 Me's in numerator)(not in MRM spreadsheet)
                ratio_peaks(., c("C30 4a Me 20S ST", "C30 4a Me 20R ST + DINO st", "C30 3B Me BB 20S ST",  "C30 3B Me 20S ST + C30 3B Me BB 20R ST", "C30 3BMe 20R ST", "C30 2aMe 20S ST", "C30 2a Me 20R + 4a Me BB 20S ST"), "allSteranes", "C30Me/allSt"),
              #DinoSt/allSt
                ratio_peaks(., c("4B Me 5a cholestane", "4B Me 24 ethyl 5a cholestane", "4B,23S,24S trimethyl 5a cholestane", "4B,23S,24R trimethyl 5a cholestane", "4B,23R,24S trimethyl 5a cholestane", "4B,23R,24R trimethyl 5a cholestane", "4a Me 5a cholestane", "4a Me 24 ethyl 5a cholestane", "4a,23S,24S trimethyl 5a cholestane", "4a,23S,24R trimethyl 5a cholestane", "4a,23R,24S trimethyl 5a cholestane", "4a,23R,24R trimethyl 5a cholestane"), "allSteranes", "DinoSt/allSt"),
           
              #C26/(C26-30)aaaSR
                ratio_peaks(., c("C26 aaa 20R ST", "C26 aaa 20S ST"), c("aaa 20R ST", "aaa 20S ST") , "C26/(C26-30)aaaSR"),
              #C27/(C26-30)aaaSR
                ratio_peaks(., c("C27 aaa 20R ST", "C27 aaa 20S ST"), c("aaa 20R ST", "aaa 20S ST") , "C27/(C26-30)aaaSR"),
              #C28/(C26-30)aaaSR
                ratio_peaks(., c("C28 aaa 20R ST", "C28 aaa 20S ST"), c("aaa 20R ST", "aaa 20S ST") , "C28/(C26-30)aaaSR"),
              #C29/(C26-30)aaaSR
                ratio_peaks(., c("C29 aaa 20R ST", "C29 aaa 20S ST"), c("aaa 20R ST", "aaa 20S ST") , "C29/(C26-30)aaaSR"),
              #C30/(C26-30)aaaSR
                ratio_peaks(., c("C30 aaa 20R ST", "C30 aaa 20S ST"), c("aaa 20R ST", "aaa 20S ST") , "C30/(C26-30)aaaSR"),
           
              #C27/C27+C28aaa&abb
                ratio_peaks(., c("C27 aaa 20R ST" , "C27 aaa 20S ST", "C27 aBB 20R ST", "C27 aBB 20S ST"), c("C27 aaa 20R ST" , "C27 aaa 20S ST", "C27 aBB 20R ST", "C27 aBB 20S ST", "C28 aaa 20R ST", "C28 aaa 20S ST", "C28 aBB 20R ST", "C28 aBB 20S ST")  , "C27/C27+C28aaa&abb"),
              #C27/C27+C29aaa&abb
                ratio_peaks(., c("C27 aaa 20R ST" , "C27 aaa 20S ST", "C27 aBB 20R ST", "C27 aBB 20S ST"), c("C27 aaa 20R ST" , "C27 aaa 20S ST", "C27 aBB 20R ST", "C27 aBB 20S ST", "C29 aaa 20R ST", "C29 aaa 20S ST", "C29 aBB 20R ST", "C29 aBB 20S ST")  , "C27/C27+C29aaa&abb"),
              #C28/C28+C27aaa&abb
                ratio_peaks(., c("C28 aaa 20R ST", "C28 aaa 20S ST", "C28 aBB 20R ST", "C28 aBB 20S ST"), c("C27 aaa 20R ST" , "C27 aaa 20S ST", "C27 aBB 20R ST", "C27 aBB 20S ST", "C28 aaa 20R ST", "C28 aaa 20S ST", "C28 aBB 20R ST", "C28 aBB 20S ST")  , "C28/C28+C27aaa&abb"),
              #C28/C28+C29aaa&abb
                ratio_peaks(., c("C28 aaa 20R ST", "C28 aaa 20S ST", "C28 aBB 20R ST", "C28 aBB 20S ST"), c("C29 aaa 20R ST", "C29 aaa 20S ST", "C29 aBB 20R ST", "C29 aBB 20S ST", "C28 aaa 20R ST", "C28 aaa 20S ST", "C28 aBB 20R ST", "C28 aBB 20S ST")  , "C28/C28+C29aaa&abb"),
              #C29/C29+C27aaa&abb
                ratio_peaks(., c("C29 aaa 20R ST", "C29 aaa 20S ST", "C29 aBB 20R ST", "C29 aBB 20S ST"), c("C27 aaa 20R ST" , "C27 aaa 20S ST", "C27 aBB 20R ST", "C27 aBB 20S ST", "C29 aaa 20R ST", "C29 aaa 20S ST", "C29 aBB 20R ST", "C29 aBB 20S ST")  , "C29/C29+C27aaa&abb"),
              #C29/C29+C28aaa&abb
                ratio_peaks(., c("C29 aaa 20R ST", "C29 aaa 20S ST", "C29 aBB 20R ST", "C29 aBB 20S ST"), c("C29 aaa 20R ST", "C29 aaa 20S ST", "C29 aBB 20R ST", "C29 aBB 20S ST", "C28 aaa 20R ST", "C28 aaa 20S ST", "C28 aBB 20R ST", "C28 aBB 20S ST")  , "C29/C29+C28aaa&abb"),
              
              #4Me_TriMe/Me_C26St
                ratio_peaks(., c("4Me_TriMe"), c("4Me_TriMe", "C26 aBB 20S ST", "C26 aBB 20R ST", "C26 aaa 20S ST", "C26 aaa 20R ST") , "4Me_TriMe/Me_C26St"),
              #4Me_TriMe/Me_C27St
                ratio_peaks(., c("4Me_TriMe"), c("4Me_TriMe", "C27 aBB 20S ST", "C27 aBB 20R ST", "C27 aaa 20S ST", "C27 aaa 20R ST") , "4Me_TriMe/Me_C27St"),
              #4Me_TriMe/Me_C28St
                ratio_peaks(., c("4Me_TriMe"), c("4Me_TriMe", "C28 aBB 20S ST", "C28 aBB 20R ST", "C28 aaa 20S ST", "C28 aaa 20R ST") , "4Me_TriMe/Me_C28St"),
              #4Me_TriMe/Me_C29St
                ratio_peaks(., c("4Me_TriMe"), c("4Me_TriMe", "C29 aBB 20S ST", "C29 aBB 20R ST", "C29 aaa 20S ST", "C29 aaa 20R ST") , "4Me_TriMe/Me_C29St"),
              #4Me_TriMe/Me_C30St
                ratio_peaks(., c("4Me_TriMe"), c("4Me_TriMe", "C30 aBB 20 R+S ST", "C30 aaa 20S ST", "C30 aaa 20R ST") , "4Me_TriMe/Me_C30St"),
              #4Me_TriMe/Me_allSt
                ratio_peaks(., c("4Me_TriMe"), c("4Me_TriMe", "allRegst") , "4Me_TriMe/Me_allSt"),
           
              #Dino/all
                ratio_peaks(., "allDiacholestane", c("allSteranes", "allRegHO"), "Dino/all"),
           
              #C26-30St/C26-C30St+regHo 
                ratio_peaks(., c("allRegst"), c("allRegst", "Ts C27 HO", "Tm C27 HO", "C27 17B HO", "29, 30 C28 bisnor HO", "28, 30 C28 bisnor HO", "C29 Ts HO", "C29 Ba HO", "C29 BB Ho", "C30 aB HO", "C30 BB HO", "C30H Ba HO", "C31 HR Ba HO", "C31 aB HR HO", "C31 aB HS HO", "C31 BB HO", "C32 aB HS HO", "C32 aB HR HO", "C33 aB HS HO", "C33 aB HR HO", "C34 aB HR HO", "C34 aB HS HO", "C35 aB HR HO", "C35 aB HS HO"), "C26-30St/C26-C30St_regHo"),
              #C27-C30aaaSt/C27-C30aaaSt+regHo
                ratio_peaks(., c( "C26 aaa 20S ST", "C26 aaa 20R ST", "C27 aaa 20S ST", "C27 aaa 20R ST", "C28 aaa 20S ST", "C28 aaa 20R ST", "C29 aaa 20S ST", "C29 aaa 20R ST", "C30 aaa 20S ST", "C30 aaa 20R ST"), c("C26 aaa 20S ST", "C26 aaa 20R ST", "C27 aaa 20S ST", "C27 aaa 20R ST", "C28 aaa 20S ST", "C28 aaa 20R ST", "C29 aaa 20S ST", "C29 aaa 20R ST", "C30 aaa 20S ST", "C30 aaa 20R ST", "allRegHO"), "C27-C30aaaSt/C27-C30aaaSt+regHo"),
              #Ho/St
                ratio_peaks(., "allRegHO", c("C26 aaa 20S ST", "C26 aaa 20R ST", "C27 aaa 20S ST", "C27 aaa 20R ST", "C28 aaa 20S ST", "C28 aaa 20R ST", "C29 aaa 20S ST", "C29 aaa 20R ST", "C30 aaa 20S ST", "C30 aaa 20R ST"), "Ho/St"),
              #Ho/St%
                ratio_peaks(., "allRegHO", c("C26 aaa 20S ST", "C26 aaa 20R ST", "C27 aaa 20S ST", "C27 aaa 20R ST", "C28 aaa 20S ST", "C28 aaa 20R ST", "C29 aaa 20S ST", "C29 aaa 20R ST", "C30 aaa 20S ST", "C30 aaa 20R ST", "allRegHO" ), "Ho/St%"),
            
              #C31_2MHI
                ratio_peaks(., "C31 2a Me Ho", c("C30 aB HO", "C31 2a Me Ho" ), "C31_2MHI"),
              #C31_35_2MHI
                ratio_peaks(., c("C31 2a Me Ho", "C32 2aMe R HO", "C32 2aMe S HO", "C33 2aMe S HO", "C33 2aMe R HO", "C34 2a Me S HO", "C34 2a Me R HO", "C36 2a Me R HO", "C36 2a Me S HO"), c("C30 aB HO", "C31 2a Me Ho", "C32 2aMe R HO", "C32 2aMe S HO", "C33 2aMe S HO", "C33 2aMe R HO", "C34 2a Me S HO", "C34 2a Me R HO", "C36 2a Me R HO", "C36 2a Me S HO"), "C31_35_2MHI"),
              #C31_2-MHI/C27-C30Steranes
                ratio_peaks(., "C31 2a Me Ho", c("C26 aaa 20S ST", "C26 aaa 20R ST", "C27 aaa 20S ST", "C27 aaa 20R ST" ,"C28 aaa 20S ST", "C28 aaa 20R ST", "C29 aaa 20S ST", "C29 aaa 20R ST", "C30 aaa 20S ST", "C30 aaa 20R ST", "C31 2a Me Ho" ), "C31_2-MHI/C27-C30Steranes"),
           
            #Thermal Maturity
              #C27_Dia/Reg
                ratio_peaks(., "C27Dia", "C27Reg", "C27Dia/Reg"),
              #C27Dia_S/R
                ratio_peaks(., "C27 aB 20S ST", "C27 aB 20R ST", "C27Dia_S/R"),
              #C27Dia_S/S+R
                ratio_peaks(., "C27 aB 20S ST", c("C27 aB 20S ST", "C27 aB 20R ST"), "C27Dia_S/S+R") ,
              #C27Reg_abb/all 
                 ratio_peaks(., c("C27 aBB 20R ST", "C27 aBB 20S ST"), c("C27 aaa 20R ST", "C27 aaa 20S ST", "C27 aBB 20R ST", "C27 aBB 20S ST"), "C27Reg_abb/aaa"),
              #C27RegaaaS/S+R
                ratio_peaks(., "C27 aaa 20S ST", c("C27 aaa 20R ST", "C27 aaa 20S ST"), "C27Regaaa_S/S+R"), 
              #C27RegabbS/S+R
                ratio_peaks(., "C27 aBB 20S ST", c("C27 aBB 20S ST", "C27 aBB 20R ST"), "C27Regabb_S/S+R"),
              #C28Dia/all
                ratio_peaks(., c("C28 Ba 20S ST", "C28 Ba 20R ST"), c("C28 aBB 20S ST", "C28 aBB 20R ST", "C28 aaa 20S ST", "C28 aaa 20R ST", "C28 Ba 20S ST", "C28 Ba 20R ST"), "C28Dia/all"),
              #C28DiaS/S+R
                ratio_peaks(., "C28 Ba 20S ST", c("C28 Ba 20S ST", "C28 Ba 20R ST"), "C28DiaS/S+R"),
              #C28abb/all
                ratio_peaks(., c("C28 aBB 20S ST", "C28 aBB 20R ST"), c("C28 aBB 20S ST", "C28 aBB 20R ST", "C28 aaa 20S ST", "C28 aaa 20R ST"), "C28abb/all"),
              #C28aaaS/S+R
                ratio_peaks(., "C28 aaa 20S ST", c("C28 aaa 20S ST", "C28 aaa 20R ST"), "C28aaaS/S+R"),
              #C28abbS/S+R
                ratio_peaks(., "C28 aBB 20S ST", c("C28 aBB 20S ST", "C28 aBB 20R ST"), "C28abbS/S+R"),
              #C29Dia/all
                ratio_peaks(., c("C29 Ba 20S ST", "C29 Ba 20R ST"),  c("C29 Ba 20S ST", "C29 Ba 20R ST", "C29 aBB 20S ST", "C29 aBB 20R ST", "C29 aaa 20S ST", "C29 aaa 20R ST"), "C29Dia/all"),
              #C29DiaS/S+R
                ratio_peaks(., "C29 Ba 20S ST", c("C29 Ba 20S ST", "C29 Ba 20R ST"), "C29DiaS/S+R"),
              #C29abb/all
                ratio_peaks(., c("C29 aBB 20S ST", "C29 aBB 20R ST"), c( "C29 aaa 20S ST", "C29 aaa 20R ST", "C29 aBB 20S ST", "C29 aBB 20R ST" ), "C29abb/all"),
              #C29aaaS/S+R
                ratio_peaks(., "C29 aaa 20S ST", c("C29 aaa 20S ST", "C29 aaa 20R ST") , "C29aaaS/S+R"),
              #C29abbS/S+R
                ratio_peaks(., "C29 aBB 20S ST", c("C29 aBB 20S ST", "C29 aBB 20R ST"), "C29abbS/S+R"),
              #C27Ts/Ts+Tm
                ratio_peaks(., "Ts C27 HO", c("Ts C27 HO", "Tm C27  HO"), "C27Ts/Tm"),
              #C28BNH29,30/28,30
                ratio_peaks(., "29, 30 C28 bisnor HO", c("29, 30 C28 bisnor HO", "28, 30 C28 bisnor HO"), "C28BNH29,30/28,30"),
              #C29Ts/Ts+ab
                ratio_peaks(., "C29 Ts HO", c( "C29 aB HO", "C29 Ts HO"), "C29Ts/ab"),
              #C29ba/ba+ab
                ratio_peaks(.,"C29 Ba HO",  c("C29 aB HO", "C29 Ba HO"), "C29ba/ab"),
              #C29bb/bb+ab
                ratio_peaks(., "C29 BB Ho", c("C29 BB Ho", "C29 aB HO"), "C29bb/ab"),
              #C30_30nor/30nor+ab
                ratio_peaks(., "30-nor C30H HO", c("C30 aB HO", "30-nor C30H HO"),  "C30_30nor/ab"),
              #C30ba/ba+ab
                ratio_peaks(., "C30H Ba HO", c("C30 aB HO", "C30H Ba HO"), "C30ba/ab"),
              #C30bb/bb+ab
                ratio_peaks(., "C30 BB HO", c("C30 aB HO", "C30 BB HO"), "C30bb/ab"),
              #C31S/S+R
                ratio_peaks(., "C31 aB HS  HO", c("C31 aB HR HO", "C31 aB HS  HO"), "C31S/S+R"),
              #C32S/S+R
                ratio_peaks(., "C32 aB HS HO", c("C32 aB HS HO", "C32 aB HR HO"), "C32S/S+R"),
              #C33S/S+R
                ratio_peaks(., "C33 aB HS HO", c("C33 aB HS HO", "C33 aB HR HO"), "C33S/S+R"),
              #C34S/S+R
                ratio_peaks(., "C34 aB HS HO", c("C34 aB HS HO", "C34 aB HR HO") , "C34S/S+R"),
              #C35S/S+R
                ratio_peaks(., "C35 aB HS HO", c("C35 aB HS HO", "C35 aB HR HO") , "C35S/S+R")
      
 ) }) %>% ungroup() 
  
final_data
```

```{r}
write.csv(final_data)
```


# Bring in other data for comparison (data from Jones et al., (2018))
```{r}
osisotope <- read_excel(file.path("metadata", "SH1_Osi_forGarrett.xlsx")) %>% 
  rename(depth = `Depth (m)`) 
```

```{r}

cisotope <- read_excel(file.path("metadata", "Appendix_Table1_geochemistry.xlsx")) %>% 
  #rename columns
  rename(depth = `Abs. depth (m)` , d13c_org = `Average δ13Corg (‰ VPDB)` , carb = `%Carbonate`, TOC = `%TOC`, d13c_carb = `Average δ13Ccarb (‰ VPDB)`) %>%
  #remove columns not of interest
  select(-`stdev δ13Corg`, -`δ13Ccarb stdev`, -`d18O-avg`, -`d18O stdev`, -`∆13C`, -`d13c_carb`)

cisotope
```

```{r "carbon isotopes", fig.width = 10, fig.height= 5}

horizontal_lines <-
  data_frame(
    depth = c(123, 120, 117)
  )

carb <- cisotope %>%
  ggplot() +
  aes(depth, carb) +
  geom_point() +
  geom_line() +
  scale_x_reverse() +
  coord_flip() +
  ggtitle("carbonate%") + 
  geom_vline(horizontal_lines,
             mapping = aes(xintercept = depth)) 


TOC <- cisotope %>%
  ggplot() +
  aes(depth, TOC) +
  geom_point() +
  geom_line() +
  scale_x_reverse() +
  coord_flip() +
  ggtitle("TOC%") +
  theme(axis.text.y = element_blank(), 
            axis.ticks.y = element_blank(), 
            axis.title.y = element_blank()) + 
  geom_vline(horizontal_lines,
             mapping = aes(xintercept = depth))


d13c <- cisotope %>%
  ggplot() +
  aes(depth, d13c_org) +
  geom_point() +
  geom_line() +
  scale_x_reverse() +
  coord_flip() +
  ggtitle("d13C_org") +
  theme(axis.text.y = element_blank(), 
            axis.ticks.y = element_blank(), 
            axis.title.y = element_blank()) + 
   geom_vline(horizontal_lines,
             mapping = aes(xintercept = depth))

os <- osisotope %>%
  ggplot() +
  aes(x = depth, y = Osi) +
  geom_point() +
  geom_line() +
  #facet_wrap(~peak_name, scales = "free") +
  scale_x_reverse() +
  coord_flip() +
  ggtitle("os") +
  #theme(axis.text.y = element_blank(), 
            #axis.ticks.y = element_blank(), 
            #axis.title.y = element_blank()) + 
  geom_vline(horizontal_lines,
             mapping = aes(xintercept = depth))

#ggplotly(carb) 
#ggplotly(TOC)
#ggplotly(d13c)

library(gridExtra)
grid.arrange(carb, TOC, d13c, os, ncol=4)
```


# Plot against depth

## Sterane - Source

### Regular steranes over all steranes
```{r "Regular steranes", fig.width = 5, fig.height = 5}
sterane_area <- subset(final_data, peak_name %in% c("C26St/allSt", "C27St/allSt", "C28St/allSt", "C29St/allSt", "C30St/allSt", "C30Me/allSt", "DinoSt/allSt")) %>%
  ggplot() +
  geom_area(mapping = aes(fill = peak_name)) +
  aes(x = depth, y = ratio, color = peak_name) +
  #facet_grid(~peak_name, scales = "free") +
  coord_flip() +
  scale_x_reverse() +
  scale_y_continuous() 

ggplotly(sterane_area)

#sterane_area_all <- grid.arrange(carb, TOC, d13c, os, sterane_area, ncol=5) 
```


### Regular aaa steranes / all regular aaa steranes 
```{r "aaaSt", fig.width = 5, fig.height = 5}
regaaa <- subset(final_data, peak_name %in% c("C26/(C26-30)aaaSR","C27/(C26-30)aaaSR", "C28/(C26-30)aaaSR", "C29/(C26-30)aaaSR", "C30/(C26-30)aaaSR")) %>%
  ggplot() +
  geom_area(mapping = aes(fill = peak_name)) +
  aes(x = depth, y = ratio, color = peak_name) +
  #facet_wrap(~peak_name, scales = "free") +
  coord_flip() +
  scale_x_reverse() +
  scale_y_continuous()  
  #theme(axis.text.y = element_blank(), 
           # axis.ticks.y = element_blank(), 
           # axis.title.y = element_blank())

ggplotly(regaaa)

#reaaa_all <- grid.arrange(d13c, regaaa, ncol=2)
```


### aaa&abb
```{r "aaa&abb", fig.width = 15, fig.height = 5}
aaa <- subset(final_data, peak_name %in% c("C27/C27+C28aaa&abb", "C27/C27+C29aaa&abb", "C28/C28+C27aaa&abb", "C28/C28+C29aaa&abb", "C29/C29+C27aaa&abb", "C29/C29+C28aaa&abb")) %>%
  ggplot() +
  geom_point() +
  geom_line() +
  #geom_area(mapping = aes(fill = peak_name)) +
  aes(x = depth, y = ratio, color = peak_name) +
  facet_grid(~peak_name) +
  coord_flip() +
  scale_x_reverse() +
  scale_y_continuous()  
  

ggplotly(aaa)

#reaaa_all <- grid.arrange( d13c, aaa, ncol=7)
```


### 4Me_TriMes
```{r "4Me_TriMes", fig.width = 15, fig.height = 5}
TriMe <- subset(final_data, peak_name %in% c("4Me_TriMe/Me_C26St", "4Me_TriMe/Me_C27St", "4Me_TriMe/Me_C28St", "4Me_TriMe/Me_C29St", "4Me_TriMe/Me_C30St", "4Me_TriMe/Me_allSt")) %>%
  ggplot() +
  geom_point() +
  geom_line() +
  #geom_area(mapping = aes(fill = peak_name)) +
  aes(x = depth, y = ratio, color = peak_name) +
  facet_grid(~peak_name) +
  coord_flip() +
  scale_x_reverse() 
ggplotly(TriMe)

```


### Sterane over all ratios
```{r "st/all", fig.width = 5, fig.height = 5}
yet <- subset(final_data, peak_name %in% c("C26-30St/C26-C30St_regHo", "C27-C30aaaSt/C27-C30aaaSt+regHo")) %>%
  ggplot() +
  aes(x = depth, y = ratio, color = peak_name) +
  geom_point() +
  geom_line() +
  facet_wrap(~peak_name, scales = "free") +
  scale_x_reverse() +
  coord_flip()
ggplotly(yet)
```

## Hopanes - Source

### Tricyclics
```{r "tri", fig.width = 10, fig.height = 5}

tri <- subset(final_data, peak_name %in% c("C19/tricyclics" , "C20/tricyclics" , "C21/tricyclics" , "C22/tricyclics" , "C23/tricyclics" , "C24/tricyclics" , "C25/tricyclics" , "C26/tricyclics")) %>%
  ggplot() +
  geom_area(mapping = aes(fill = peak_name)) +
  aes(x = depth, y = ratio, color = peak_name) +
  #facet_wrap(~peak_name, scales = "free") +
  scale_x_reverse() +
  coord_flip()
  
ggplotly(tri)
```


```{r "", fig.width = 8, fig.height = 5}
tri_all <- subset(final_data, peak_name %in% c("C19/C19+23",  "C20/C20+23", "tricyclics/all")) %>%
  ggplot() +
  aes(x = depth, y = ratio) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~peak_name, scales = "free") +
  scale_x_reverse() +
  coord_flip()
ggplotly(tri_all)
```


### Hopanes over steranes
```{r "Ho/St", fig.width = 5, fig.height = 5}
vertical_lines <- data_frame(
    one = 1
  )

host <- subset(final_data, peak_name == "Ho/St") %>%
  ggplot() +
  aes(x = depth, y = ratio) +
  geom_point() +
  geom_line() +
  facet_wrap(~peak_name, scales = "free") +
  geom_hline(vertical_lines,
             mapping = aes(yintercept = one)) +
  scale_x_reverse() +
  coord_flip() 
  

ggplotly(host)
```


### 2Me Hopanes
```{r "", fig.width = 8, fig.height = 5}
mehi <- subset(final_data, peak_name %in% c("C31_2MHI", "C31_35_2MHI", "C31_2-MHI/C27-C30Steranes"))%>%
  ggplot() +
  aes(x = depth, y = ratio, color = peak_name) +
  geom_point() +
  geom_line() +
  facet_wrap(~peak_name, scales = "free") +
  scale_x_reverse() +
  coord_flip()
ggplotly(mehi)
```


### 3Me Hopanes
```{r "C31 3-MHI", fig.width = 8, fig.height = 5}
threemehi <- subset(final_data, peak_name %in% c( "C31_35_3MHI(%)", "C31 3-MHI")) %>%
  ggplot() +
  aes(x = depth, y = ratio) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~peak_name, scales = "free") +
  scale_x_reverse() +
  coord_flip()
ggplotly(threemehi)
```


### C29 aB Hopane
```{r "twentynineho", fig.width = 8, fig.height = 5}
abs <- subset(final_data, peak_name%in% c("C29ab/allHoab", "C29ab/C29ab+C30ab")) %>%
  filter(ratio > 0.1) %>%
  ggplot() +
  aes(x = depth, y = ratio) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~peak_name, scales = "free") +
  scale_x_reverse() +
  coord_flip()
ggplotly(abs)
```

### ab/all ho
```{r "ab/all ho", fig.width = 8, fig.height = 5}
ho <- subset(final_data, peak_name %in% c("C29ab/allHoab","C30ab/allHoab", "C31ab/allHoab", "C32ab/allHoab", "C33ab/allHoab", "C34ab/allHoab", "C35ab/allHoab")) %>%
   ggplot() +
  geom_area(mapping = aes(fill = peak_name)) +
  aes(x = depth, y = ratio, color = peak_name) +
  #facet_wrap(~peak_name, scales = "free") +
  coord_flip() +
  scale_x_reverse() +
  scale_y_continuous() 
ggplotly(ho)

```

### Stratification
```{r "HHI and GI", fig.width = 8, fig.height = 5}
HHIGI <- subset(final_data, peak_name %in% c( "GI", "HHI")) %>%
  ggplot() +
  aes(x = depth, y = ratio) +
  geom_point() +
  geom_line() +
  facet_wrap(~peak_name, scales = "free") +
  scale_x_reverse() +
  coord_flip()
ggplotly(HHIGI)
```

### Miscelaneous Hopane ratios
```{r "OleananeIndex", fig.width = 5, fig.height = 5}
subset(final_data, peak_name== "OleananeIndex") %>%
  ggplot() +
  aes(x = depth, y = ratio) +
  geom_point() +
  geom_line() +
 # facet_wrap(~peak_name, scales = "free") +
  scale_x_reverse() +
  coord_flip()
```


```{r "C35/C35+C34", fig.width = 5, fig.height = 5}
subset(final_data, peak_name== "C35/C35+C34") %>%
  ggplot() +
  aes(x = depth, y = ratio) +
  geom_point() +
  geom_line() +
  facet_wrap(~peak_name, scales = "free") +
  scale_x_reverse() +
  coord_flip()
```


```{r "28,30BNH/28,30BNH+C30", fig.width = 5, fig.height = 5}
subset(final_data, peak_name== "28,30BNH/28,30BNH+C30") %>%
  ggplot() +
  aes(x = depth, y = ratio) +
  geom_point() +
  geom_line()+
  facet_wrap(~peak_name, scales = "free") +
  scale_x_reverse() +
  coord_flip()
```


## Thermal Maturity

### C27Dia/Reg
```{r "", fig.width = 5, fig.height = 5}
dia <- subset(final_data, peak_name == "C27Dia/Reg") %>%
  ggplot() +
  aes(x = depth, y = ratio) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~peak_name, scales = "free") +
  scale_x_reverse() +
  coord_flip()

ggplotly(dia)
```


### DiaS/S+R
```{r "diasr", fig.width = 5, fig.height = 5}
diasr <- subset(final_data, peak_name%in% c("C28DiaS/S+R" , "C29DiaS/S+R")) %>%
  filter(depth != 116.490) %>% filter(depth != 116.900) %>%
  ggplot() +
  aes(x = depth, y = ratio, color = peak_name) +
  geom_point() +
  geom_line() +
  #facet_wrap(~peak_name, scales = "free") +
  scale_x_reverse() +
  coord_flip()

ggplotly(diasr)
```


### C27Regabb/aaa
```{r "C27Regabb/aaa", fig.width = 5, fig.height = 5}
twentyseven<- subset(final_data, peak_name== "C27Reg_abb/aaa") %>%
  filter(depth != 115.885) %>%
  ggplot() +
  aes(x = depth, y = ratio) +
  geom_line() +
  geom_point() +
  facet_wrap(~peak_name, scales = "free") +
  scale_x_reverse() +
  coord_flip()

ggplotly(twentyseven)
```


### aaa_S/S+R
```{r "aaa_S/S+R", fig.width = 8, fig.height = 5}
aaa<- final_data %>%
  filter(peak_name %in% c("C27Regaaa_S/S+R", "C28aaaS/S+R", "C29aaaS/S+R")) %>%
  filter(depth != 115.885) %>%
  ggplot() +
  aes(x = depth, y = ratio, color = peak_name) +
  geom_line() +
  geom_point() +
  facet_grid(~peak_name, scales = "free") +
  scale_x_reverse() +
  coord_flip()

ggplotly(aaa)
```


### abb_s/s+r
```{r "", fig.width = 8, fig.height = 5}
abb <- subset(final_data, peak_name %in% c("C27Regabb_S/S+R", "C28abbS/S+R", "C29abbS/S+R")) %>%
  filter(depth != 115.885) %>%
  ggplot() +
  aes(x = depth, y = ratio, color = peak_name) +
  geom_point() +
  #facet_wrap(~peak_name, scales = "free") +
  scale_x_reverse() +
  coord_flip()

ggplotly(abb)
```


### C28/9Dia/all
```{r "", fig.width = 8, fig.height = 5}
Dia <- subset(final_data, peak_name %in% c("C28Dia/all", "C29Dia/all")) %>%
  ggplot() +
  aes(x = depth, y = ratio, color = peak_name) +
  geom_point() +
  geom_line() +
  #facet_wrap(~peak_name, scales = "free") +
  scale_x_reverse() +
  coord_flip()

ggplotly(Dia)
```


### C28/9abb/all
```{r "C28/9abb/all", fig.width = 8, fig.height = 5}
eightnine <- subset(final_data, peak_name %in% c("C28abb/all", "C29abb/all"))  %>%
  filter(depth != 115.885) %>%
  ggplot() +
  aes(x = depth, y = ratio, color = peak_name) +
  geom_point() +
  geom_line() +
  #facet_wrap(~peak_name, scales = "free") +
  scale_x_reverse() +
  coord_flip() 

ggplotly(eightnine)
```


### C27Ts/Tm
```{r "", fig.width = 5, fig.height = 5}
tstm <- subset(final_data, peak_name== "C27Ts/Tm") %>%
  filter(depth != 115.885) %>% filter(depth != 120.405) %>%
  ggplot() +
  aes(x = depth, y = ratio) +
  geom_point() +
  geom_line() +
  facet_wrap(~peak_name, scales = "free") +
  scale_x_reverse() +
  coord_flip()
ggplotly(tstm)
```


### C28BNH29,30/28,30
```{r "C28BNH29,30/28,30", fig.width = 5, fig.height = 5}
bnh <- subset(final_data, peak_name== "C28BNH29,30/28,30") %>%
  ggplot() +
  aes(x = depth, y = ratio) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~peak_name, scales = "free") +
  scale_x_reverse() +
  coord_flip()
ggplotly(bnh)
```

### C29Ts/ab
```{r "", fig.width = 5, fig.height = 5}
tsab<- subset(final_data, peak_name== "C29Ts/ab") %>%
  ggplot() +
  aes(x = depth, y = ratio) +
  geom_point() +
  geom_line() +
  facet_wrap(~peak_name, scales = "free") +
  scale_x_reverse() +
  coord_flip()
ggplotly(tsab)
```

### C29,30ba/ab
```{r "C29,30ba/ab", fig.width = 5, fig.height = 5}
baab <- subset(final_data, peak_name %in% c("C29ba/ab", "C30ba/ab")) %>%
  ggplot() +
  aes(x = depth, y = ratio, color = peak_name) +
  geom_point() +
  geom_line() +
  #facet_wrap(~peak_name, scales = "free") +
  scale_x_reverse() +
  coord_flip()

ggplotly(baab)
```

### C29bb/ab
```{r "C29bb/ab", fig.width = 5, fig.height = 5}
bbab <- subset(final_data, peak_name %in% c("C29bb/ab", "C30bb/ab")) %>%
  ggplot() +
  aes(x = depth, y = ratio, color = peak_name) +
  geom_point() +
  geom_line() +
  #facet_wrap(~peak_name, scales = "free") +
  scale_x_reverse() +
  coord_flip()
ggplotly(bbab)
```

### C30_30nor/ab
```{r "C30_30nor/ab", fig.width = 5, fig.height = 5}
thirtynor <- subset(final_data, peak_name== "C30_30nor/ab") %>%
  ggplot() +
  aes(x = depth, y = ratio) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~peak_name, scales = "free") +
  scale_x_reverse() +
  coord_flip()
ggplotly(thirtynor)
```

### C30 ab/ba
```{r "C30 HOs", fig.width = 5, fig.height = 5}
thabba <- subset(final_data, peak_name %in% c("C30 aB HO", "C30H Ba HO")) %>%
  ggplot() +
  aes(x = depth, y = conc_rock.ug_g, color = peak_name) +
  geom_point() + 
  geom_line() +
  #facet_wrap(~peak_name) +
  scale_x_reverse() +
  coord_flip()
ggplotly(thabba)
```


### All Ho S/R
```{r "All Ho S/R", fig.width = 10, fig.height = 5}
srho <- final_data %>%
  filter(peak_name %in% c("C31S/S+R", "C32S/S+R", "C33S/S+R", "C34S/S+R", "C35S/S+R")) %>%
  filter(ratio > 0.1) %>%
  ggplot() +
  aes(x = depth, y = ratio, color = peak_name) +
  geom_point() +
  geom_line() +
  #facet_grid(~peak_name) +
  scale_x_reverse() +
  coord_flip()
ggplotly(srho)
```


### Everything
```{r "everything", fig.width = 5, fig.height = 5}
erry <- final_data %>%
  filter(peak_name == "everything") %>%
  ggplot() +
  aes(x = depth, y = conc_rock.ug_g) +
  geom_point() +
  geom_line() +
  #facet_grid(~peak_name) +
  scale_x_reverse() +
  coord_flip()
ggplotly(erry)
```


### Chunk to check plots
```{r}
outcome <- calib_data %>% 
  group_by(file_id) %>%
  select(file_id, peak_name, depth, area.cpm, conc_rock.ug_g) %>% 
  do({
    bind_rows(., 
            ratio_peaks(., "C27 aB 20S ST", "C27 aB 20R ST", "C27Dia_S/R")
    )
  }) %>% 
  filter(#!str_detect(file_id, "TSQ3779"),  
         str_detect(peak_name, "C27 aB 20R ST")) 
         #str_detect(peak_name, "aB"))
outcome
```