---
title: "2018_Ari_aliphatic_thermalmaturity"
output: html_document
---
# Start up functions
```{r "cleanup", echo = FALSE, eval=FALSE}
# not run in knitted doc
rm(list = ls())
.rs.restartR()
```

```{r "load libraries", echo = FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(plotly)
library(stringr)
library(knitr)
library(readxl)
library(tidyr)
library(purrr)
library(xlsx)
opts_chunk$set(dev=c("png", "pdf"), dev.args=list(pdf = list(encoding="WinAnsi", useDingbats=FALSE)),
  fig.keep="all", fig.path = file.path("plots", "MSC_SRM")) ### CHANGE PLOT SUFFIX ###
```

# Read and organize data
```{r}
read_srm_export <- function(filename, columns = c("peak_name", "RT.min", "basepeak", "area.cpm", "height.cts", "quantitation")) {
  filename %>% 
    # read excel files
    read_excel(sheet = "Integration", skip = 42, 
               col_names = columns, col_types = rep("text", length(columns))) %>% 
    as_data_frame() %>%
    # remove empty rows
    filter(!is.na(peak_name), peak_name != "n.a.") %>% 
    # convert the relevant numeric columns into numbers
    mutate_at(vars(RT.min, area.cpm, height.cts), as.numeric) %>% 
    # remove useless columns
    select(-basepeak, -quantitation) %>% 
    # add filename info
    mutate(file_id = gsub("\\.xls", "", basename(filename))) %>% 
    select(file_id, everything())
}

# get data
all_data <- 
  # find all excel files ##change name and use new folder for new project
  list.files("data_ari", recursive = TRUE, full.names = TRUE, pattern = "\\.xls$") %>% 
  # send them to the read method
  lapply(read_srm_export) %>% 
  # combine the data set
  bind_rows() %>% 
  # pull out sample information
  #mutate(sample_id = str_match(all_data$file_id, "TSQ\\d+_GB_(.*)$") %>% { .[,2] }) %>% 
  # get n replicates
  group_by(file_id)
  #mutate(n_replicates = length(unique(file_id)))

```

## File names for metadata file
```{r, echo=FALSE, eval=FALSE}
# file names
all_data$file_id %>% unique() %>%  paste(collapse = "\n") %>% message()
```

#Plot to check the spread
##by sequence
```{r "all area"}
all_data %>% 
  ggplot() + 
  aes(x = peak_name, y = area.cpm, color = file_id) +
  geom_point(size = 3) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```
##by sample
```{r}
all_data %>% 
  ggplot() +
  aes(x = file_id, y = area.cpm, color = file_id) + 
  geom_point(size = 3) +
  facet_wrap(~peak_name, scales = "free_y") +
    theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
        legend.position = "none")
```

# Calculation peak amounts and rock concentrations, ID standards

```{r}
depth_and_rock_info <- read_excel(file.path("metadata", "aliphaticSRM_MSC.xlsx")) %>% 
  rename(tle = `TLE.mg`, maltene = `maltenes.mg`, ref_amount_added.ug = `D4.ug` ) %>% 
  filter(!is.na(file_id))
kable(depth_and_rock_info)
```

```{r}
data_by_depth <- 
  all_data %>%
  left_join(depth_and_rock_info, by = "file_id") %>% 
  group_by(file_id) %>% 
  mutate(
    n_peaks = n(),
    n_standards = sum(peak_name == "D4 C29 ISTD"),
    ref_area.cpm = area.cpm[peak_name == "D4 C29 ISTD"],
    amount.ug = area.cpm/ref_area.cpm * ref_amount_added.ug,
   
    #Normalize by what you want
    conc_rock.ug_g = amount.ug / rock.g, 
    conc_tle.ug.g = amount.ug / tle,  
    conc_maltene.ug.g = amount.ug / maltene
    
  )%>% ungroup() %>% 
  arrange(file_id, peak_name) 

data_by_depth
```

# Calculate Recovery

### Linear regressions of the calibration curves

```{r}
standard <- read_excel(file.path("metadata", "D4_calibration.xlsx"))   ###read excel

###calibration curve
standard %>% 
  ggplot() +
  aes(x = Known.ng, y = Measured_area.counts, color = calibration) + 
  geom_smooth(method = "lm", alpha = 0.5) +
  geom_point() +
  theme_bw() +
  theme(legend.position = "none") 
 
calibrations <- 
  standard %>% 
  filter(!is.na(calibration)) %>% 
  nest(-calibration) %>% 
  mutate(
    fit = map(data, ~summary(lm(`Measured_area.counts`~ `Known.ng`, data = .x))),
    coefficients = map(fit, "coefficients"),
    intercept = map_dbl(coefficients, `[`, 1, 1),
    intercept_se = map_dbl(coefficients, `[`, 1, 2),
    slope = map_dbl(coefficients, `[`, 2, 1),
    slope_se = map_dbl(coefficients, `[`, 2, 2),
    r2 = map_dbl(fit, "r.squared")
  )
```

### Determine yield

These numbers are not useful for anything else.

```{r}
calib_data <-
  data_by_depth %>% 
  # temp
  mutate(calibration = "jan2018") %>% 
  left_join(calibrations, by = "calibration") %>% 
  mutate(
    total_volume.uL = 100,
    total_inject.uL = 1.5,
    ref_amount_inject_expected.ng = (ref_amount_added.ug * 1000)/total_volume.uL * total_inject.uL ,
    ref_amount_inject_measured.ng = (ref_area.cpm - intercept)/slope,
    ref_amount_measured.ug = ((total_volume.uL* ref_amount_inject_measured.ng)/total_inject.uL) * 1/1000,
    yield = (ref_amount_inject_measured.ng/ref_amount_inject_expected.ng) * 100
  )
  
calib_data
```

#### check yields

```{r}
calib_data %>% 
  select(file_id, peak_name, yield)  %>% 
  arrange(file_id)  %>% 
  unique() %>% 
  ggplot() + aes(file_id, y = yield) +
  geom_point(size = 3) +
  theme_bw() + theme(axis.text.x = element_text(angle = 90, hjust = 0, vjust = 0.5))
```


#Combine compounds/make ratios (new rows w/o RTs etc, just concentration.rock column)

```{r}
# functions to make it easy to sum up peaks

sum_peaks <- function(df, filter_condition, new_peak_name) {
  filter_condition <- sprintf("(%s)", str_c(filter_condition, collapse = "|"))
  filter(df, str_detect(peak_name, filter_condition)) %>% 
    summarize(
      file_id = file_id[1],
      depth = depth[1],
      conc_rock.ug_g = sum(conc_rock.ug_g)
    ) %>% 
    mutate(peak_name = new_peak_name)
}

ratio_peaks <- function(df, filter_top, filter_bottom, new_peak_name) {
  filter_top <- sprintf("(%s)", str_c(filter_top, collapse = "|"))
  filter_bottom <- sprintf("(%s)", str_c(filter_bottom, collapse = "|"))
  filter(df, str_detect(peak_name, filter_top) | str_detect(peak_name, filter_bottom)) %>% 
    summarize(
      file_id = file_id[1],
      depth = depth[1],
      ratio = sum(conc_rock.ug_g[str_detect(peak_name, filter_top)]) / sum(conc_rock.ug_g[str_detect(peak_name, filter_bottom)])
    ) %>% 
    mutate(peak_name = new_peak_name)
}
```

##Ideas for other ratios? What about dimethyls?
```{r}
#set values to use for later calculations
final_data1 <- calib_data %>% 
    group_by(file_id) %>% 
        do({
          bind_rows(., 
              #C27_Dia/Reg
                sum_peaks(.,  c("C27 aB 20R ST", "C27 aB 20S ST"), "C27Dia"),      
                sum_peaks(., c("C27 aaa 20R ST", "C27 aaa 20S ST", "C27 aBB 20R ST", "C27 aBB 20S ST", "C27 Ba 20R ST", "C27 Ba 20S ST"), "C27Reg"),
            
              #Total Tricyclics
                sum_peaks(., c("C19 Tri HO", "C20 Tri HO", "C21 Tri HO", "C22 Tri HO", "C23 Tri HO", "C24 Tet HO", "C24 Tri HO", "C25 Tri R HO", "C25 Tri S HO", "C26 Tri R HO", "C26 Tri S HO"), "all_tricyclics"),
            
              #4Me_TriMe
                sum_peaks(., c("4B Me 5a cholestane", "4B Me 24 ethyl 5a cholestane", "4B,23S,24S trimethyl 5a cholestane", "4B,23S,24R trimethyl 5a cholestane", "4B,23R,24S trimethyl 5a cholestane", "4B,23R,24R trimethyl 5a cholestane", "4a Me 5a cholestane", "4a Me 24 ethyl 5a cholestane", "4a,23S,24S trimethyl 5a cholestane", "4a,23S,24R trimethyl 5a cholestane", "4a,23R,24S trimethyl 5a cholestane", "4a,23R,24R trimethyl 5a cholestane"), "4Me_TriMe"),
            
              #allRegSt
                sum_peaks(., c("C26 aBB 20S ST", "C26 aBB 20R ST", "C26 aaa 20S ST", "C26 aaa 20R ST","C27 aBB 20S ST", "C27 aBB 20R ST", "C27 aaa 20S ST", "C27 aaa 20R ST", "C28 aBB 20S ST", "C28 aBB 20R ST", "C28 aaa 20S ST", "C28 aaa 20R ST","C29 aBB 20S ST", "C29 aBB 20R ST", "C29 aaa 20S ST", "C29 aaa 20R ST", "C30 aBB 20 R+S ST", "C30 aaa 20S ST", "C30 aaa 20R ST"), "allRegst"),
            
              #allRegHO
                sum_peaks(., c("Ts C27 HO", "Tm C27 HO", "C27 17B H Ho", "29, 30 C28H bisnor HO", "28, 30 C28 bisnor HO", "C29 Ts HO", "C29 Ba HO", "C29 BB Ho", "C30 aB HO", "C30 BB HO", "C30H Ba HO", "C31 HR Ba HO", "C31 aB HR HO", "C31 aB HS HO", "C31 BB HO", "C32 aB HS HO", "C32 aB HR HO", "C33 aB HS HO", "C33 aB HR HO", "C34 aB HR HO", "C34 aB HS HO", "C35 aB HR HO", "C35 aB HS HO"), "allRegHO") 
            
) }) %>% ungroup()

```
            
```{r}
final_data <- final_data1 %>% 
    group_by(file_id) %>% 
        do({
          bind_rows(., 
            #Thermal Maturity
              #C27_Dia/Reg
                ratio_peaks(., "C27Dia", "C27Reg", "C27Dia/Reg"),
              #C27Dia_S/R
                ratio_peaks(., "C27 aB 20S ST", c("C27 aB 20R ST", "C27 aB 20S ST"), "C27Dia_S/R"),
              #C27Reg_abb/all 
                 ratio_peaks(., c("C27 aBB 20R ST", "C27 aBB 20S ST"), c("C27 aaa 20R ST", "C27 aaa 20S ST", "C27 aBB 20R ST", "C27 aBB 20S ST"), "C27Reg_abb/aaa"),
              #C27RegaaaS/S+R
                ratio_peaks(., "C27 aaa 20S ST", c("C27 aaa 20R ST", "C27 aaa 20S ST"), "C27Regaaa_S/S+R"), 
              #C27RegabbS/S+R
                ratio_peaks(., "C27 aBB 20S ST", c("C27 aBB 20S ST", "C27 aBB 20R ST"), "C27Regabb_S/S+R"),
              #C28Dia/all
                ratio_peaks(., c("C28 Ba 20S ST", "C28 Ba 20R ST"), c("C28 aBB 20S ST", "C28 aBB 20R ST", "C28 aaa 20S ST", "C28 aaa 20R ST", "C28 Ba 20S ST", "C28 Ba 20R ST"), "C28Dia/all"),
              #C28DiaS/S+R
                ratio_peaks(., "C28 Ba 20S ST", c("C28 Ba 20S ST", "C28 Ba 20R ST"), "C28DiaS/S+R"),
              #C28abb/all
                ratio_peaks(., c("C28 aBB 20S ST", "C28 aBB 20R ST"), c("C28 aBB 20S ST", "C28 aBB 20R ST", "C28 aaa 20S ST", "C28 aaa 20R ST"), "C28abb/all"),
              #C28aaaS/S+R
                ratio_peaks(., "C28 aaa 20S ST", c("C28 aaa 20S ST", "C28 aaa 20R ST"), "C28aaaS/S+R"),
              #C28abbS/S+R
                ratio_peaks(., "C28 aBB 20S ST", c("C28 aBB 20S ST", "C28 aBB 20R ST"), "C28abbS/S+R"),
              #C29Dia/all
                ratio_peaks(., c("C29 Ba 20S ST", "C29 Ba 20R ST"),  c("C29 Ba 20S ST", "C29 Ba 20R ST", "C29 aBB 20S ST", "C29 aBB 20R ST", "C29 aaa 20S ST", "C29 aaa 20R ST"), "C29Dia/all"),
              #C29DiaS/S+R
                ratio_peaks(., "C29 Ba 20S ST", c("C29 Ba 20S ST", "C29 Ba 20R ST"), "C29DiaS/S+R"),
              #C29abb/all
                ratio_peaks(., c("C29 aBB 20S ST", "C29 aBB 20R ST"), c( "C29 aaa 20S ST", "C29 aaa 20R ST", "C29 aBB 20S ST", "C29 aBB 20R ST" ), "C29abb/all"),
              #C29aaaS/S+R
                ratio_peaks(., "C29 aaa 20S ST", c("C29 aaa 20S ST", "C29 aaa 20R ST") , "C29aaaS/S+R"),
              #C29abbS/S+R
                ratio_peaks(., "C29 aBB 20S ST", c("C29 aBB 20S ST", "C29 aBB 20R ST"), "C29abbS/S+R"),
              #C27Ts/Ts+Tm
                ratio_peaks(., "Ts C27 HO", c("Ts C27 HO", "Tm C27  HO"), "C27Ts/Tm"),
              #C28BNH29,30/28,30
                ratio_peaks(., "29, 30 C28 bisnor HO", c("29, 30 C28 bisnor HO", "28, 30 C28 bisnor HO"), "C28BNH29,30/28,30"),
              #C29Ts/Ts+ab
                ratio_peaks(., "C29 Ts HO", c( "C29 aB HO", "C29 Ts HO"), "C29Ts/ab"),
              #C29ba/ba+ab
                ratio_peaks(.,"C29 Ba HO",  c("C29 aB HO", "C29 Ba HO"), "C29ba/ab"),
              #C29bb/bb+ab
                ratio_peaks(., "C29 BB Ho", c("C29 BB Ho", "C29 aB HO"), "C29bb/ab"),
              #C30_30nor/30nor+ab
                ratio_peaks(., "30-nor C30H HO", c("C30 aB HO", "30-nor C30H HO"),  "C30_30nor/ab"),
              #C30ba/ba+ab
                ratio_peaks(., "C30H Ba HO", c("C30 aB HO", "C30H Ba HO"), "C30ba/ab"),
              #C30bb/bb+ab
                ratio_peaks(., "C30 BB HO", c("C30 aB HO", "C30 BB HO"), "C30bb/ab"),
              #C31S/S+R
                ratio_peaks(., "C31 aB HS  HO", c("C31 aB HR HO", "C31 aB HS  HO"), "C31S/S+R"),
              #C32S/S+R
                ratio_peaks(., "C32 aB HS HO", c("C32 aB HS HO", "C32 aB HR HO"), "C32S/S+R"),
              #C33S/S+R
                ratio_peaks(., "C33 aB HS HO", c("C33 aB HS HO", "C33 aB HR HO"), "C33S/S+R"),
              #C34S/S+R
                ratio_peaks(., "C34 aB HS HO", c("C34 aB HS HO", "C34 aB HR HO") , "C34S/S+R"),
              #C35S/S+R
                ratio_peaks(., "C35 aB HS HO", c("C35 aB HS HO", "C35 aB HR HO") , "C35S/S+R")
          
              
 ) }) %>% ungroup() 
  
final_data
```

```{r}
 write.table(final_data, file = "Arifinaldata.csv")
```


# Against depth

## ratios etc

###C27Dia/Reg
```{r "", fig.width = 5, fig.height = 5}
subset(final_data, peak_name== "C27Dia/Reg") %>%
  ggplot() +
  aes(x = ratio, y = depth) +
  geom_point() +
  facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```


```{r "", fig.width = 5, fig.height = 5}
diareg <- subset(final_data, peak_name %in% c("C27Dia", "C27Reg")) %>%
  ggplot() +
  aes(x = conc_rock.ug_g, y = depth, color = peak_name) +
  geom_point() +
  #facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
ggplotly(diareg)
```
```{r}
# test checks
outcome <- calib_data %>% 
  group_by(file_id) %>%
  select(file_id, peak_name, depth, area.cpm, conc_rock.ug_g) %>% 
  do({
    bind_rows(., 
        ratio_peaks(., "C27 aB 20R ST", "C27 aB 20S ST", "C27Dia_S/R")
    )
  }) %>% 
  filter(#!str_detect(file_id, "TSQ3779"),  
         str_detect(peak_name, "C27Dia_S/R")) 
         #str_detect(peak_name, "aB"))
outcome
```

###DiaS/S+R
```{r "diasr", fig.width = 5, fig.height = 5}
diasr <- final_data %>% 
  filter(peak_name %in% c("C27Dia_S/R" , "C28DiaS/S+R" , "C29DiaS/S+R")) %>%
  ggplot() +
  aes(x = ratio, y = depth, color = peak_name) +
  geom_point() +
  #facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
ggplotly(diasr)
```

```{r "", fig.width = 5, fig.height = 5}
subset(final_data, peak_name== c("C27 aB 20R ST", "C27 aB 20S ST")) %>%
  ggplot() +
  aes(x = conc_rock.ug_g, y = depth, color = peak_name) +
  geom_point() +
  #facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```


###C27Regabb/aaa
```{r "", fig.width = 5, fig.height = 5}
subset(final_data, peak_name== "C27Reg_abb/aaa") %>%
  ggplot() +
  aes(x = ratio, y = depth) +
  geom_point() +
  facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```
#aaa_S/S+R
```{r "", fig.width = 5, fig.height = 5}
final_data %>%
  filter(peak_name == c("C27Regaaa_S/S+R", "C28aaaS/S+R", "C29aaaS/S+R")) %>%
  ggplot() +
  aes(x = ratio, y = depth, color = peak_name) +
  geom_point() +
  #facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```
###abb_s/s+r
```{r "", fig.width = 5, fig.height = 5}
subset(final_data, peak_name == c("C27Regabb_S/S+R", "C28abbS/S+R", "C29abbS/S+R")) %>%
  ggplot() +
  aes(x = ratio, y = depth, color = peak_name) +
  geom_point() +
  #facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```


###C28/9Dia/all
```{r "", fig.width = 5, fig.height = 5}
Dia <- subset(final_data, peak_name== c("C28Dia/all", "C29Dia/all")) %>%
  ggplot() +
  aes(x = ratio, y = depth, color = peak_name) +
  geom_point() +
  #facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
ggplotly(Dia)
```


#C28/9abb/all
```{r "", fig.width = 5, fig.height = 5}
subset(final_data, peak_name == c("C28abb/all", "C29abb/all"))  %>%
  ggplot() +
  aes(x = ratio, y = depth, color = peak_name) +
  geom_point() +
  #facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```

#C28aaaS/S+R
```{r "", fig.width = 10, fig.height = 8}
subset(final_data, peak_name== "C28aaaS/S+R") %>%
  ggplot() +
  aes(x = ratio, y = depth) +
  geom_point() +
  facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```

#C28abbS/S+R
```{r "", fig.width = 10, fig.height = 8}
subset(final_data, peak_name== "C28abbS/S+R") %>%
  ggplot() +
  aes(x = ratio, y = depth) +
  geom_point() +
  facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```

```{r "", fig.width = 10, fig.height = 8}
subset(final_data, peak_name == c("C28 aBB 20R ST", "C28 aBB 20S ST") ) %>%
  ggplot() +
  aes(x = conc_rock.ug_g, y = depth, color = peak_name) +
  geom_point() +
  facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```

#C29Dia/all
```{r "", fig.width = 10, fig.height = 8}
subset(final_data, peak_name== "C29Dia/all") %>%
  ggplot() +
  aes(x = ratio, y = depth) +
  geom_point() +
  facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```

#C29DiaS/S+R
```{r "", fig.width = 10, fig.height = 8}
subset(final_data, peak_name== "C29DiaS/S+R") %>%
  ggplot() +
  aes(x = ratio, y = depth) +
  geom_point() +
  facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```

```{r "", fig.width = 10, fig.height = 8}
subset(final_data, peak_name == c("C29 Ba 20R ST", "C29 Ba 20S ST") ) %>%
  ggplot() +
  aes(x = conc_rock.ug_g, y = depth, color = peak_name) +
  geom_point() +
  facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```

#C29abb/all
```{r "", fig.width = 10, fig.height = 8}
subset(final_data, peak_name== "C29abb/all") %>%
  ggplot() +
  aes(x = ratio, y = depth) +
  geom_point() +
  facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```

#C29aaaS/S+R
```{r "", fig.width = 10, fig.height = 8}
subset(final_data, peak_name== "C29aaaS/S+R") %>%
  ggplot() +
  aes(x = ratio, y = depth) +
  geom_point() +
  facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```

#C29abbS/S+R
```{r "", fig.width = 10, fig.height = 8}
subset(final_data, peak_name== "C29abbS/S+R") %>%
  ggplot() +
  aes(x = ratio, y = depth) +
  geom_point() +
  facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```

#C27Ts/Tm
```{r "", fig.width = 10, fig.height = 8}
subset(final_data, peak_name== "C27Ts/Tm") %>%
  ggplot() +
  aes(x = ratio, y = depth) +
  geom_point() +
  facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```

```{r "Tsm", fig.width = 10, fig.height = 8}
tsm <- subset(final_data, peak_name == c("Ts C27 HO", "Tm C27  HO") ) %>%
  ggplot() +
  aes(x = conc_rock.ug_g, y = depth, color = peak_name) +
  geom_point() +
  #facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
ggplot(tsm)
```

#C28BNH29,30/28,30
```{r "", fig.width = 10, fig.height = 8}
subset(final_data, peak_name== "C28BNH29,30/28,30") %>%
  ggplot() +
  aes(x = ratio, y = depth) +
  geom_point() +
  facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```

#C29Ts/ab
```{r "", fig.width = 10, fig.height = 8}
subset(final_data, peak_name== "C29Ts/ab") %>%
  ggplot() +
  aes(x = ratio, y = depth) +
  geom_point() +
  facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```

#C29,30ba/ab
```{r "", fig.width = 10, fig.height = 8}
subset(final_data, peak_name== c("C29ba/ab", "C30ba/ab")) %>%
  ggplot() +
  aes(x = ratio, y = depth, color = peak_name) +
  geom_point() +
  #facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```

#C29bb/ab
```{r "", fig.width = 10, fig.height = 8}
subset(final_data, peak_name == c("C29bb/ab", "C30bb/ab")) %>%
  ggplot() +
  aes(x = ratio, y = depth, color = peak_name) +
  geom_point() +
  #facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```

#C30_30nor/ab
```{r "", fig.width = 5, fig.height = 5}
subset(final_data, peak_name== "C30_30nor/ab") %>%
  ggplot() +
  aes(x = ratio, y = depth) +
  geom_point() +
  facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```

#C30ba/ab
```{r "", fig.width = 5, fig.height = 5}
subset(final_data, peak_name== "C30ba/ab") %>%
  ggplot() +
  aes(x = ratio, y = depth) +
  geom_point() +
  facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```



```{r "", fig.width = 5, fig.height = 5}
abba <- final_data %>% 
  filter(peak_name == c("C30H Ba HO", "C30 aB HO")) %>%
  group_by(file_id) %>%
  ggplot() +
  aes(x = conc_rock.ug_g, y = depth, color = peak_name) +
  geom_point() +
  #facet_wrap(~peak_name) +
  scale_y_reverse()
ggplotly(abba)

```

```{r "", fig.width = 5, fig.height = 5}
subset(final_data, peak_name == c("C30 aB HO", "C30H Ba HO")) %>%
  ggplot() +
  aes(x = area.cpm, y = depth, color = peak_name) +
  geom_point() +
  #facet_wrap(~peak_name) +
  scale_y_reverse()

```




#C30bb/ab
```{r "", fig.width = 10, fig.height = 8}
subset(final_data, peak_name== "C30bb/ab") %>%
  ggplot() +
  aes(x = ratio, y = depth) +
  geom_point() +
  facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```

#All Ho S/R
```{r "", fig.width = 5, fig.height = 10}
srho <- final_data %>%
  filter(peak_name == c("C31S/S+R", "C32S/S+R", "C33S/S+R", "C34S/S+R", "C35S/S+R")) %>%
  ggplot() +
  aes(x = ratio, y = depth, color = peak_name) +
  geom_point() +
  #facet_wrap(~peak_name, scales = "free") 
  scale_y_reverse()
ggplotly(srho)
```


#C31S/S+R
```{r "", fig.width = 10, fig.height = 8}
subset(final_data, peak_name== "C31S/S+R") %>%
  ggplot() +
  aes(x = ratio, y = depth) +
  geom_point() +
  facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```

#C32S/S+R
```{r "", fig.width = 10, fig.height = 8}
subset(final_data, peak_name== "C32S/S+R") %>%
  ggplot() +
  aes(x = ratio, y = depth) +
  geom_point() +
  facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```

#C33S/S+R
```{r "", fig.width = 10, fig.height = 8}
subset(final_data, peak_name== "C33S/S+R") %>%
  ggplot() +
  aes(x = ratio, y = depth) +
  geom_point() +
  facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```

#C34S/S+R
```{r "", fig.width = 10, fig.height = 8}
subset(final_data, peak_name== "C34S/S+R") %>%
  ggplot() +
  aes(x = ratio, y = depth) +
  geom_point() +
  facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```

#C35S/S+R
```{r "", fig.width = 10, fig.height = 8}
subset(final_data, peak_name== "C35S/S+R") %>%
  ggplot() +
  aes(x = ratio, y = depth) +
  geom_point() +
  facet_wrap(~peak_name, scales = "free") +
  scale_y_reverse()
```






```{r}
final_data <- createWorkbook()
data.frame(final_data)
#addDataFrame(x=data, sheet=final_data)
saveWorkbook(final_datas, "Ari_finaldata.xlsx")

```

```{r}
write.csv(final_data, "final_data.csv")
```

```{r}
write.excel <- function(x,row.names=FALSE,col.names=TRUE,...) {
  write.table(x,"clipboard",sep="\t",row.names=row.names,col.names=col.names,...)
}

write.excel(final_data)
```

